


# Appendix A

## Reliability of adaptive tests and the lengths that were used in Experiment 1, according to their original publications.

```{r}

tibble::tibble(
  Test = c("JaJ", "MDT", "PIAT", "PDCT", "MPT"),
  `No. Items` = c(8, 11, 15, 15, 15),
  Reliability = c("~.78","~.62", "~.60", "Not known", "~.60"),
  `Reliability Type` = c("Empirical", "Test-retest", "Test-retest", "Not known", "Test-retest")
) %>% 
  knitr::kable(caption = "Reliability of adaptive tests")

```

Note that estimates are approximate due to being read off graphs visually.

# Appendix B

## Melodic features


```{r warning = FALSE}

itembankr::get_melodic_feature_table(features = c("target_melody_length", "i.entropy", 'step.cont.loc.var', 'd.entropy', 'log_freq'),
                                     return_kable = FALSE) %>% 
  mutate(Feature = case_when(Feature == "target_melody_length" ~ "N", TRUE ~ Feature)) %>% 
  knitr::kable(escape = FALSE)

```

\newpage

# Appendix C

## SAA Dependent Variables

```{r}

SAA_dvs <- tibble::tibble(
  Measure = c("ngrukkon", "harmcore", "rhythfuzz", "opti3", "no_note_events", "no_correct*", "no_errors", "proportion_of_correct_note_events*", "proportion_of_correct_note_events_controlled_by_stimuli_length_log_normal*", "proportion_of_stimuli_notes_found*"),
  Definition = c("Ukkonen measures for N-grams on raw pitch values",
                 "Edit Distance of harmonic symbols per segment, obtained via Krumhansl’s tonality vectors.",
                 "Edit distance of classified length of melody tones.", "3.027 * ngrukkon + 2.502 * rhythfuzz + 1.439 * harmcore", "The number of notes the participant produced in the trial.", "The number of correct notes the participant sang.", "The number of errors participants sang.", "The proportion of note events which were correct.", "As above, but scaled to [0,1] using the log normal function", "The proportion of notes contained in the stimuli that were produced in the trial."))

papaja::apa_table(SAA_dvs, caption = "Full set of dependent variables produced by the SAA.", 
          note = "* this measure has an ‘octaves allowed’ partner, which compares pitch classes rather than MIDI pitches. Hence, it does not matter what octave something is sung in. Variable names use snake case, corresponding to their naming inside the SAA software.")



```





# Appendix D

## Comparison of internal vs. external microphone selection

When comparing the effect of using an internal vs. external microphone, as self-selected by the user at the beginning of entry to the *SAA*, our results suggest there is no difference in *opti3* scores.

```{r, fig.cap = "Boxplot, dotplot and SEM plot of opti3 for self-reported microphone type", warning = FALSE}

ggplot(dat, aes(reorder(microphone_type,opti3),opti3,fill=microphone_type)) +
  geom_jitter(colour = "dark gray",width=.1) +
  stat_boxplot(geom ='errorbar',width = 0.4) +
  geom_boxplot()+
  labs(x = "Microphone Type",
       y = "opti3") +
  guides(fill=FALSE) +
  theme_bw()

```



```{r}

mictype.aov <- aov(opti3~microphone_type, dat)

mictype.ttest <- dat %>% 
  filter(microphone_type != "Not sure") %>% 
  t.test(opti3~microphone_type, data = .)


opti3_internal <- dat %>% 
  filter(microphone_type == "Internal") %>% 
  summarise(m = mean(opti3, na.rm = TRUE),
            sd = sd(opti3, na.rm = TRUE))
  
opti3_external <- dat %>% 
  filter(microphone_type == "External") %>% 
  summarise(m = mean(opti3, na.rm = TRUE),
            sd = sd(opti3, na.rm = TRUE))


```

A one-way ANOVA revealed that there was only just no statistically significant difference in *opti3* scores between at least two microphone type groups, including "Not sure" (F(2, 11437) = 2.90, *p* = 0.054). Similarly, there was no significant effect for microphone type when assessing the difference between reported only internal and external microphones via an unpaired samples t-test, t(11437) = 0.97, p = .097, despite external microphones (*M* = `r round(opti3_external$m, 3)`, *SD* = `r round(opti3_external$sd, 2)`) attaining fractionally higher *opti3* scores than internal microphones (*M* = `r round(opti3_internal$m, 3)`, *SD* = `r round(opti3_internal$sd, 2)`). This suggests that the combination of *pYIN* and *opti3* in our analysis pipeline are robust to the important feature of microphone type in a user's setup.


 

